---
title: "Validating CHTC data extraction"
author: "Jessalyn Ayars"
date: "2022-08-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(geodiv)
library(raster)
library(sf)
select <- dplyr::select
```

## plan

do separately for each metric and xsf
generate random list of rows to check (set seed)
iterate over check size (start with 10, 10 is fine imo)
  
  iterate over scale (6)
  visually check output

### data/params
```{r}
rsf.scales <- read_csv(here("data-private", "gps_rsf_scales.csv")) %>%
  select(-n_ap, -data)
scales <- c(0, 30, 60, 120, 300, 500)
```


## RSF checks
- aspect all yrs: 1 or 2 very slightly off, no evidence of logical errors
```{r rsf-aspect}
set.seed(81022)
row.checks <- sample(nrow(rsf.scales), 10)

check.a <- rsf.scales[row.checks,1:13]  %>%
				st_as_sf(coords = c("x_", "y_"), crs = 32610, remove = F) %>%
				st_transform(4269) %>%
				mutate(lon = unlist(map(geometry,1)),
						lat = unlist(map(geometry,2))) 

aspect <- raster(here("data-private", "snb_aspect.tif"))

for (scale in scales) {
		newvar <- extract(aspect, check.a[, c("lon", "lat")], fun = mean, buffer = scale, weights = T)
		check.a <- cbind(check.a, newvar) 
}
```

- cc 2015/16: good
```{r rsf-cc}
set.seed(81722)
rsf.20156 <- filter(rsf.scales, Year == "2015" | Year == "2016")
row.checks <- sample(nrow(rsf.20156), 10)

check.b <- rsf.20156[row.checks,1:19]

cc <- raster(here("data-private", "cfo_canopycover_summer_2016.tif"))

for (scale in scales) {
  newvar <- extract(cc, check.b[, c("x_", "y_")], fun = mean, buffer = scale, weights = T)
	check.b <- cbind(check.b, newvar) 
}
```

- ch 2017: perfect
```{r rsf-ch}
set.seed(111)
rsf.2017 <- filter(rsf.scales, Year == "2017")
row.checks <- sample(nrow(rsf.2017), 10)

check.c <- rsf.2017[row.checks, 1:25]
ch <- raster(here("data-private", "cfo_canopyheight_summer_2017.tif"))

for (scale in scales) {
  newvar <- extract(ch, check.c[, c("x_", "y_")], fun = mean, buffer = scale, weights = T)
	check.c <- cbind(check.c, newvar) 
}
```

- lfd 2015/16: perfect
```{r rsf-lfd}
set.seed(222)
row.checks <- sample(nrow(rsf.20156), 10)

check.d <- rsf.20156[row.checks,1:31]
lfd <- raster(here("data-private", "cfo_ladderfueldensity_summer_2016.tif"))

for (scale in scales) {
  newvar <- extract(lfd, check.d[, c("x_", "y_")], fun = mean, buffer = scale, weights = T)
	check.d <- cbind(check.d, newvar) 
}
```

- s10z 2017: perfct matches!!!
```{r rsf-s10z}
set.seed(333)
row.checks <- sample(nrow(rsf.2017), 10)

check.e <- rsf.2017[row.checks,2:36]
ch.2017 <- ch

scale = scales[4] # change and check
  check.temp <- check.e %>%
			st_as_sf(coords = c("x_", "y_"), crs = 32610) %>%
			st_buffer(scale)
  newvar <- list()
	for (j in 1:nrow(check.temp)) {
		mini.extent <- extent(check.temp[j,])
		mini.raster <- crop(ch.2017, mini.extent)
		result <- s10z(mini.raster) 
		newvar <- rbind(newvar, result)
	}
  newvar <- as_tibble(newvar)
	check.e <- cbind(check.temp, newvar) %>%
		mutate(newvar = unlist(V1), .keep = "unused")
```

- sci for 2015/16: all in order
```{r rsf-sci}
set.seed(81822)
row.checks <- sample(nrow(rsf.20156), 10)

ch.20156 <- raster(here("data-private", "cfo_canopyheight_summer_2016.tif"))

check.f <- rsf.20156[row.checks, c(2:8, 37:42)]

scale = scales[6] # change and check
  check.temp <- check.f %>%
			st_as_sf(coords = c("x_", "y_"), crs = 32610) %>%
			st_buffer(scale)
  newvar <- list()
	for (j in 1:nrow(check.temp)) {
		mini.extent <- extent(check.temp[j,])
		mini.raster <- crop(ch.20156, mini.extent)
		result <- sci(mini.raster) 
		newvar <- rbind(newvar, result)
	}
  newvar <- as_tibble(newvar)
	check.f <- cbind(check.temp, newvar) %>%
		mutate(newvar = unlist(V1), .keep = "unused")
```

- sdq for 2017: all g!!
```{r rsf-sdq}
set.seed(555)
row.checks <- sample(nrow(rsf.2017), 10)

check.g <- rsf.2017[row.checks,c(2:8, 42:46)]

scale = scales[6] # change and check
  check.temp <- check.g %>%
			st_as_sf(coords = c("x_", "y_"), crs = 32610) %>%
			st_buffer(scale)
  newvar <- list()
	for (j in 1:nrow(check.temp)) {
		mini.extent <- extent(check.temp[j,])
		mini.raster <- crop(ch.2017, mini.extent)
		result <- sdq(mini.raster) 
		newvar <- rbind(newvar, result)
	}
  newvar <- as_tibble(newvar)
	check.g <- cbind(check.temp, newvar) %>%
		mutate(newvar = unlist(V1), .keep = "unused")
```

- sf for 2015/16: perfect
```{r rsf-sf}
set.seed(444)
row.checks <- sample(nrow(rsf.20156), 10)

check.h <- rsf.20156[row.checks,c(1:8,47:52)]
sf <- raster(here("data-private", "cfo_surfacefuels_summer_2016.tif"))

for (scale in scales) {
  newvar <- extract(sf, check.h[, c("x_", "y_")], fun = mean, buffer = scale, weights = T)
	check.h <- cbind(check.h, newvar) 
}
```

- sq for 2017: perfect        
```{r}
set.seed(666)
row.checks <- sample(nrow(rsf.2017), 10)

check.i <- rsf.2017[row.checks,c(2:8, 52:57)]

scale = scales[2] # change and check
  check.temp <- check.i %>%
			st_as_sf(coords = c("x_", "y_"), crs = 32610) %>%
			st_buffer(scale)
  newvar <- list()
	for (j in 1:nrow(check.temp)) {
		mini.extent <- extent(check.temp[j,])
		mini.raster <- crop(ch.2017, mini.extent)
		result <- sq(mini.raster) 
		newvar <- rbind(newvar, result)
	}
  newvar <- as_tibble(newvar)
	check.i <- cbind(check.temp, newvar) %>%
		mutate(newvar = unlist(V1), .keep = "unused")
```


## SSF checks

### data
```{r}
ssf.hr <- read_csv(here("data-private", "gps_ssf_hr_scales.csv"))
ssf.min <- read_csv(here("data-private", "gps_ssf_min_scales.csv"))
ssf.2019 <- filter(ssf.min, Year == "2019")
ssf.2020 <- filter(ssf.min, Year == "2020")
```

### checks

- aspect: ssf.hr, solid
```{r ssf-aspect}
set.seed(81922)
row.checks <- sample(nrow(ssf.hr), 10)

check.j <- ssf.hr[row.checks,c(1:9,16:21)]  %>%
				st_as_sf(coords = c("x2_", "y2_"), crs = 32610, remove = F) %>%
				st_transform(4269) %>%
				mutate(lon = unlist(map(geometry,1)),
						lat = unlist(map(geometry,2))) 

aspect <- raster(here("data-private", "snb_aspect.tif"))

for (scale in scales) {
		newvar <- extract(aspect, check.j[, c("lon", "lat")], fun = mean, buffer = scale, weights = T)
		check.j <- cbind(check.j, newvar) 
}
```

- cc: ssf.min for 2019, all g
```{r ssf-cc}
set.seed(777)
row.checks <- sample(nrow(ssf.2019), 10)

check.k <- ssf.2019[row.checks,c(1:9,22:27)]

cc.2019 <- raster(here("data-private", "cfo_canopycover_summer_2019.tif"))

for (scale in scales) {
  newvar <- extract(cc.2019, check.k[, c("x2_", "y2_")], fun = mean, buffer = scale, weights = T)
	check.k <- cbind(check.k, newvar) 
}
```

- ch: ssf.min for 2020, good
```{r ssf-ch}
set.seed(888)
row.checks <- sample(nrow(ssf.2020), 10)

check.l <- ssf.2020[row.checks, c(1:9, 28:33)]

ch.2020 <- raster(here("data-private", "cfo_canopyheight_summer_2020.tif"))

for (scale in scales) {
  newvar <- extract(ch.2020, check.l[,c("x2_", "y2_")], fun = mean, buffer = scale, weights = T)
  check.l <- cbind(check.l, newvar)
}
```

- lfd: ssf.hr for 2018, good
```{r ssf-lfd}
set.seed(999)
ssf.2018 <- filter(ssf.hr, Year == "2018")
row.checks <- sample(nrow(ssf.2018), 10)

check.m <- ssf.2018[row.checks, c(1:9, 34:39)]

lfd.2018 <- raster(here("data-private", "cfo_ladderfueldensity_summer_2018.tif"))

for (scale in scales) {
  newvar <- extract(lfd.2018, check.m[,c("x2_", "y2_")], fun = mean, buffer = scale, weights = T)
  check.m <- cbind(check.m, newvar)
}
```

- s10z: ssf.hr for 2017
```{r ssf-s10z}
set.seed(3546)
ssf.2017 <- filter(ssf.hr, Year == "2017")
row.checks <- sample(nrow(ssf.2017), 10)

ch.2017 <- raster(here("data-private", "cfo_canopyheight_summer_2017.tif"))

check.n <- ssf.2017[row.checks, c(1:9, 40:45)]

scale = scales[3] # change and check
  check.temp <- check.n %>%
			st_as_sf(coords = c("x2_", "y2_"), crs = 32610) %>%
			st_buffer(scale)
  newvar <- list()
	for (j in 1:nrow(check.temp)) {
		mini.extent <- extent(check.temp[j,])
		mini.raster <- crop(ch.2017, mini.extent)
		result <- s10z(mini.raster) 
		newvar <- rbind(newvar, result)
	}
  newvar <- as_tibble(newvar)
	check.n <- cbind(check.temp, newvar) %>%
		mutate(newvar = unlist(V1), .keep = "unused")
```

- sci: ssf.min for 2019
```{r ssf-sci}
set.seed(7658)
row.checks <- sample(nrow(ssf.2019), 10)

ch.2019 <- raster(here("data-private", "cfo_canopyheight_summer_2019.tif"))

check.o <- ssf.2019[row.checks, c(1:9, 45:49)]

scale = scales[6] # change and check
  check.temp <- check.o %>%
			st_as_sf(coords = c("x2_", "y2_"), crs = 32610) %>%
			st_buffer(scale)
  newvar <- list()
	for (j in 1:nrow(check.temp)) {
		mini.extent <- extent(check.temp[j,])
		mini.raster <- crop(ch.2019, mini.extent)
		result <- sci(mini.raster) 
		newvar <- rbind(newvar, result)
	}
  newvar <- as_tibble(newvar)
	check.o <- cbind(check.temp, newvar) %>%
		mutate(newvar = unlist(V1), .keep = "unused")
```

- sdq: ssf.min for 2020, good
```{r ssf-sdq}
set.seed(3214)
row.checks <- sample(nrow(ssf.2020), 10)

check.p <- ssf.2020[row.checks, c(1:9, 50:54)]

scale = scales[2] # change and check
  check.temp <- check.p %>%
			st_as_sf(coords = c("x2_", "y2_"), crs = 32610) %>%
			st_buffer(scale)
  newvar <- list()
	for (j in 1:nrow(check.temp)) {
		mini.extent <- extent(check.temp[j,])
		mini.raster <- crop(ch.2020, mini.extent)
		result <- sdq(mini.raster) 
		newvar <- rbind(newvar, result)
	}
  newvar <- as_tibble(newvar)
	check.p <- cbind(check.temp, newvar) %>%
		mutate(newvar = unlist(V1), .keep = "unused")
```

- sf: ssf.hr for 2017, perfect
```{r ssf-sf}
set.seed(45678)
row.checks <- sample(nrow(ssf.2017), 10)

check.q <- ssf.2017[row.checks, c(1:9, 55:60)]

sf.2017 <- raster(here("data-private", "cfo_surfacefuels_summer_2017.tif"))

for (scale in scales) {
  newvar <- extract(sf.2017, check.q[,c("x2_", "y2_")], fun = mean, buffer = scale, weights = T)
  check.q <- cbind(check.q, newvar)
}
```

- extra checks: sf for mxm ssf for 2019 AND 2020 bc it looks weird
```{r}
set.seed(0902)

row.checks <- sample(nrow(ssf.2019), 15)
check.q2 <- ssf.2019[row.checks, c(1:9, 55:60)]
sf.2019 <- raster(here("data-private", "cfo_surfacefuels_summer_2019.tif"))

for (scale in scales) {
  newvar <- extract(sf.2019, check.q2[,c("x2_", "y2_")], fun = mean, buffer = scale, weights = T)
  check.q2 <- cbind(check.q2, newvar)
} # good


set.seed(09021)

row.checks <- sample(nrow(ssf.2020), 15)
check.q3 <- ssf.2020[row.checks, c(1:9, 55:60)]
sf.2020 <- raster(here("data-private", "cfo_surfacefuels_summer_2020.tif"))

for (scale in scales) {
  newvar <- extract(sf.2020, check.q3[,c("x2_", "y2_")], fun = mean, buffer = scale, weights = T)
  check.q3 <- cbind(check.q3, newvar)
} # also good!
```


- sq: ssf.hr for 2018: perfect
```{r ssf-sq}
set.seed(7899)
row.checks <- sample(nrow(ssf.2018), 10)

ch.2018 <- raster(here("data-private", "cfo_canopyheight_summer_2018.tif"))

check.r <- ssf.2018[row.checks, c(1:9, 61:65)]

scale = scales[6] # change and check
  check.temp <- check.r %>%
			st_as_sf(coords = c("x2_", "y2_"), crs = 32610) %>%
			st_buffer(scale)
  newvar <- list()
	for (j in 1:nrow(check.temp)) {
		mini.extent <- extent(check.temp[j,])
		mini.raster <- crop(ch.2018, mini.extent)
		result <- sq(mini.raster) 
		newvar <- rbind(newvar, result)
	}
  newvar <- as_tibble(newvar)
	check.r <- cbind(check.temp, newvar) %>%
		mutate(newvar = unlist(V1), .keep = "unused")
```

