---
title: "multi-scale optimization for minute-ly SSF"
author: "Jessalyn Ayars"
date: "2022-08-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(glmmTMB)
```

goal: get it to converge across all scales, no matter how simple the model has to be
1. switch optimizers
2. reduce size of lfv
3. don't fix variance

### data
```{r}
ssf.min.scales <- read_csv(here("data-public", "gps_ssf_min_scales.csv"))  %>%
  mutate(across(cc.0:sq.60, ~ as.numeric(scale(.x)))) %>%
  mutate(id = str_c(Territory, ".", Year)) %>%
  mutate(step.id.id = str_c(id, ".", step_id_))
```

## models

goal: get it to converge across all scales, no matter how simple the model has to be
1. switch optimizers
2. reduce size of lfv
3. don't fix variance
4. drop random effects

### canopy cover
```{r}
cc.0 = glmmTMB(case_ ~ cc.0 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
cc.0$parameters$theta[1] = log(1e3) 
cc.0$mapArg = list(theta=factor(c(NA, 1))) 
cc.0 = glmmTMB:::fitTMB(cc.0) 
summary(cc.0) 

cc.30 = glmmTMB(case_ ~ cc.30 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
cc.30$parameters$theta[1] = log(1e3) 
cc.30$mapArg = list(theta=factor(c(NA, 1))) 
cc.30 = glmmTMB:::fitTMB(cc.30) 
summary(cc.30) 

cc.60 = glmmTMB(case_ ~ cc.60 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
cc.60$parameters$theta[1] = log(1e3) 
cc.60$mapArg = list(theta=factor(c(NA, 1))) 
cc.60 = glmmTMB:::fitTMB(cc.60) 
summary(cc.60) 

cc.120 = glmmTMB(case_ ~ cc.120 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
cc.120$parameters$theta[1] = log(1e3) 
cc.120$mapArg = list(theta=factor(c(NA, 1))) 
cc.120 = glmmTMB:::fitTMB(cc.120) 
summary(cc.120) 

cc.300 = glmmTMB(case_ ~ cc.300 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
cc.300$parameters$theta[1] = log(1e3) 
cc.300$mapArg = list(theta=factor(c(NA, 1))) 
cc.300 = glmmTMB:::fitTMB(cc.300) 
summary(cc.300) 

cc.500 = glmmTMB(case_ ~ cc.500 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
cc.500$parameters$theta[1] = log(1e3) 
cc.500$mapArg = list(theta=factor(c(NA, 1))) 
cc.500 = glmmTMB:::fitTMB(cc.500) 
summary(cc.500) 

anova(cc.0, cc.30, cc.60, cc.120, cc.300, cc.500) # 60
```

### canopy height
```{r}
ch.0 = glmmTMB(case_ ~ ch.0 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
ch.0$parameters$theta[1] = log(1e3) 
ch.0$mapArg = list(theta=factor(c(NA, 1))) 
ch.0 = glmmTMB:::fitTMB(ch.0) 
summary(ch.0) 

ch.30 = glmmTMB(case_ ~ ch.30 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
ch.30$parameters$theta[1] = log(1e3) 
ch.30$mapArg = list(theta=factor(c(NA, 1))) 
ch.30 = glmmTMB:::fitTMB(ch.30) 
summary(ch.30) 

ch.60 = glmmTMB(case_ ~ ch.60 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
ch.60$parameters$theta[1] = log(1e3) 
ch.60$mapArg = list(theta=factor(c(NA, 1))) 
ch.60 = glmmTMB:::fitTMB(ch.60) 
summary(ch.60) 

ch.120 = glmmTMB(case_ ~ ch.120 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
ch.120$parameters$theta[1] = log(1e3) 
ch.120$mapArg = list(theta=factor(c(NA, 1))) 
ch.120 = glmmTMB:::fitTMB(ch.120) 
summary(ch.120) 

ch.300 = glmmTMB(case_ ~ ch.300 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
ch.300$parameters$theta[1] = log(1e3) 
ch.300$mapArg = list(theta=factor(c(NA, 1))) 
ch.300 = glmmTMB:::fitTMB(ch.300) 
summary(ch.300) 

ch.500 = glmmTMB(case_ ~ ch.500 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
ch.500$parameters$theta[1] = log(1e3) 
ch.500$mapArg = list(theta=factor(c(NA, 1))) 
ch.500 = glmmTMB:::fitTMB(ch.500) 
summary(ch.500) 

anova(ch.0, ch.30, ch.60, ch.120, ch.300, ch.500) # 60
```

### lfd
```{r}
lfd.0 = glmmTMB(case_ ~ lfd.0 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
lfd.0$parameters$theta[1] = log(1e3) 
lfd.0$mapArg = list(theta=factor(c(NA, 1))) 
lfd.0 = glmmTMB:::fitTMB(lfd.0) 
summary(lfd.0) 

lfd.30 = glmmTMB(case_ ~ lfd.30 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
lfd.30$parameters$theta[1] = log(1e3) 
lfd.30$mapArg = list(theta=factor(c(NA, 1))) 
lfd.30 = glmmTMB:::fitTMB(lfd.30) 
summary(lfd.30) 

lfd.60 = glmmTMB(case_ ~ lfd.60 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
lfd.60$parameters$theta[1] = log(1e3) 
lfd.60$mapArg = list(theta=factor(c(NA, 1))) 
lfd.60 = glmmTMB:::fitTMB(lfd.60) 
summary(lfd.60) 

lfd.120 = glmmTMB(case_ ~ lfd.120 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
lfd.120$parameters$theta[1] = log(1e3) 
lfd.120$mapArg = list(theta=factor(c(NA, 1))) 
lfd.120 = glmmTMB:::fitTMB(lfd.120) 
summary(lfd.120) 

lfd.300 = glmmTMB(case_ ~ lfd.300 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
lfd.300$parameters$theta[1] = log(1e3) 
lfd.300$mapArg = list(theta=factor(c(NA, 1))) 
lfd.300 = glmmTMB:::fitTMB(lfd.300) 
summary(lfd.300) 

lfd.500 = glmmTMB(case_ ~ lfd.500 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
lfd.500$parameters$theta[1] = log(1e3) 
lfd.500$mapArg = list(theta=factor(c(NA, 1))) 
lfd.500 = glmmTMB:::fitTMB(lfd.500) 
summary(lfd.500) 

anova(lfd.0, lfd.30, lfd.60, lfd.120, lfd.300, lfd.500) # 300 is best
```

### s10z
```{r}
s10z.30 = glmmTMB(case_ ~ s10z.30 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
s10z.30$parameters$theta[1] = log(1e3) 
s10z.30$mapArg = list(theta=factor(c(NA, 1))) 
s10z.30 = glmmTMB:::fitTMB(s10z.30) 
summary(s10z.30) 

s10z.60 = glmmTMB(case_ ~ s10z.60 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
s10z.60$parameters$theta[1] = log(1e3) 
s10z.60$mapArg = list(theta=factor(c(NA, 1))) 
s10z.60 = glmmTMB:::fitTMB(s10z.60) 
summary(s10z.60) 

s10z.120 = glmmTMB(case_ ~ s10z.120 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
s10z.120$parameters$theta[1] = log(1e3) 
s10z.120$mapArg = list(theta=factor(c(NA, 1))) 
s10z.120 = glmmTMB:::fitTMB(s10z.120) 
summary(s10z.120) 

s10z.300 = glmmTMB(case_ ~ s10z.300 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
s10z.300$parameters$theta[1] = log(1e3) 
s10z.300$mapArg = list(theta=factor(c(NA, 1))) 
s10z.300 = glmmTMB:::fitTMB(s10z.300) 
summary(s10z.300) 

s10z.500 = glmmTMB(case_ ~ s10z.500 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
s10z.500$parameters$theta[1] = log(1e3) 
s10z.500$mapArg = list(theta=factor(c(NA, 1))) 
s10z.500 = glmmTMB:::fitTMB(s10z.500) 
summary(s10z.500) 

anova(s10z.30, s10z.60, s10z.120, s10z.300, s10z.500) # 60
```

### sci
```{r}
sci.30 = glmmTMB(case_ ~ sci.30 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sci.30$parameters$theta[1] = log(1e3) 
sci.30$mapArg = list(theta=factor(c(NA, 1))) 
sci.30 = glmmTMB:::fitTMB(sci.30) 
summary(sci.30) 

sci.60 = glmmTMB(case_ ~ sci.60 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sci.60$parameters$theta[1] = log(1e3) 
sci.60$mapArg = list(theta=factor(c(NA, 1))) 
sci.60 = glmmTMB:::fitTMB(sci.60) 
summary(sci.60) 

sci.120 = glmmTMB(case_ ~ sci.120 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sci.120$parameters$theta[1] = log(1e3) 
sci.120$mapArg = list(theta=factor(c(NA, 1))) 
sci.120 = glmmTMB:::fitTMB(sci.120) 
summary(sci.120) 

sci.300 = glmmTMB(case_ ~ sci.300 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sci.300$parameters$theta[1] = log(1e3) 
sci.300$mapArg = list(theta=factor(c(NA, 1))) 
sci.300 = glmmTMB:::fitTMB(sci.300) 
summary(sci.300) 

sci.500 = glmmTMB(case_ ~ sci.500 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sci.500$parameters$theta[1] = log(1e3) 
sci.500$mapArg = list(theta=factor(c(NA, 1))) 
sci.500 = glmmTMB:::fitTMB(sci.500) 
summary(sci.500) 

anova(sci.30, sci.60, sci.120, sci.300, sci.500) # 60
```

### sdq
```{r}
sdq.30 = glmmTMB(case_ ~ sdq.30 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sdq.30$parameters$theta[1] = log(1e3) 
sdq.30$mapArg = list(theta=factor(c(NA, 1))) 
sdq.30 = glmmTMB:::fitTMB(sdq.30) 
summary(sdq.30) 

sdq.60 = glmmTMB(case_ ~ sdq.60 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sdq.60$parameters$theta[1] = log(1e3) 
sdq.60$mapArg = list(theta=factor(c(NA, 1))) 
sdq.60 = glmmTMB:::fitTMB(sdq.60) 
summary(sdq.60) 

sdq.120 = glmmTMB(case_ ~ sdq.120 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sdq.120$parameters$theta[1] = log(1e3) 
sdq.120$mapArg = list(theta=factor(c(NA, 1))) 
sdq.120 = glmmTMB:::fitTMB(sdq.120) 
summary(sdq.120) 

sdq.300 = glmmTMB(case_ ~ sdq.300 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sdq.300$parameters$theta[1] = log(1e3) 
sdq.300$mapArg = list(theta=factor(c(NA, 1))) 
sdq.300 = glmmTMB:::fitTMB(sdq.300) 
summary(sdq.300) 

sdq.500 = glmmTMB(case_ ~ sdq.500 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sdq.500$parameters$theta[1] = log(1e3) 
sdq.500$mapArg = list(theta=factor(c(NA, 1))) 
sdq.500 = glmmTMB:::fitTMB(sdq.500) 
summary(sdq.500) 

anova(sdq.30, sdq.60, sdq.120, sdq.300, sdq.500) # 30
```

### sf
```{r}
sf.0 = glmmTMB(case_ ~ sf.0 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sf.0$parameters$theta[1] = log(1e3) 
sf.0$mapArg = list(theta=factor(c(NA, 1))) 
sf.0 = glmmTMB:::fitTMB(sf.0) 
summary(sf.0) 

sf.30 = glmmTMB(case_ ~ sf.30 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sf.30$parameters$theta[1] = log(1e3) 
sf.30$mapArg = list(theta=factor(c(NA, 1))) 
sf.30 = glmmTMB:::fitTMB(sf.30) 
summary(sf.30) 

sf.60 = glmmTMB(case_ ~ sf.60 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sf.60$parameters$theta[1] = log(1e3) 
sf.60$mapArg = list(theta=factor(c(NA, 1))) 
sf.60 = glmmTMB:::fitTMB(sf.60) 
summary(sf.60) 

sf.120 = glmmTMB(case_ ~ sf.120 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sf.120$parameters$theta[1] = log(1e3) 
sf.120$mapArg = list(theta=factor(c(NA, 1))) 
sf.120 = glmmTMB:::fitTMB(sf.120) 
summary(sf.120) 

sf.300 = glmmTMB(case_ ~ sf.300 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sf.300$parameters$theta[1] = log(1e3) 
sf.300$mapArg = list(theta=factor(c(NA, 1))) 
sf.300 = glmmTMB:::fitTMB(sf.300) 
summary(sf.300) 

sf.500 = glmmTMB(case_ ~ sf.500 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sf.500$parameters$theta[1] = log(1e3) 
sf.500$mapArg = list(theta=factor(c(NA, 1))) 
sf.500 = glmmTMB:::fitTMB(sf.500) 
summary(sf.500) 

anova(sf.0, sf.30, sf.60, sf.120, sf.300, sf.500) # 60
```

### sq
```{r}
sq.30 = glmmTMB(case_ ~ sq.30 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sq.30$parameters$theta[1] = log(1e3) 
sq.30$mapArg = list(theta=factor(c(NA, 1))) 
sq.30 = glmmTMB:::fitTMB(sq.30) 
summary(sq.30) 

sq.60 = glmmTMB(case_ ~ sq.60 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sq.60$parameters$theta[1] = log(1e3) 
sq.60$mapArg = list(theta=factor(c(NA, 1))) 
sq.60 = glmmTMB:::fitTMB(sq.60) 
summary(sq.60) 

sq.120 = glmmTMB(case_ ~ sq.120 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sq.120$parameters$theta[1] = log(1e3) 
sq.120$mapArg = list(theta=factor(c(NA, 1))) 
sq.120 = glmmTMB:::fitTMB(sq.120) 
summary(sq.120) 

sq.300 = glmmTMB(case_ ~ sq.300 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sq.300$parameters$theta[1] = log(1e3) 
sq.300$mapArg = list(theta=factor(c(NA, 1))) 
sq.300 = glmmTMB:::fitTMB(sq.300) 
summary(sq.300) 

sq.500 = glmmTMB(case_ ~ sq.500 + (1|step.id.id) + (1|id), 
                       family=poisson, data= ssf.min.scales, doFit=FALSE) 
sq.500$parameters$theta[1] = log(1e3) 
sq.500$mapArg = list(theta=factor(c(NA, 1))) 
sq.500 = glmmTMB:::fitTMB(sq.500) 
summary(sq.500) 

anova(sq.30, sq.60, sq.120, sq.300, sq.500) # 30
```


## data set for official hourly SSF modeling
```{r}
ssf.min.final <- read_csv(here("data-public", "gps_ssf_min_scales.csv")) %>%
  dplyr::select(Territory, usfws_id, Year, burst_, case_, sl_, ta_, t1_, t2_, dt_, step_id_, cc.60, ch.60, lfd.300, s10z.60, sci.60, sdq.30, sf.60, sq.30) %>%
  mutate(across(cc.60:sq.30, ~ as.numeric(scale(.x)), .names = "{.col}.scaled")) %>%
  mutate(id = str_c(Territory, ".", Year)) %>%
  mutate(step.id.id = str_c(id, ".", step_id_)) 

write_csv(ssf.min.final, here("data-public", "ssf_min_final.csv"))
```
